%-------------------------
% Resume in Latex
% Author : Shajal Ahamed
% Website: 
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\usepackage{fontawesome}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{ https://www.linkedin.com/in/shajal-ahamed-277a3379/}{\Large Shajal Ahamed}} & Email : \href{mailto:shajalahamedcse@gmail.com}{shajalahamedcse@gmail.com}
  
  \\
  \href{https://www.airasia.com/en/gb}{DevOps Engineer(II) at AirAsia.} & Mobile : +8801620256783 \\
  
  \href{https://www.linkedin.com/in/shajal-ahamed-277a3379/}{\faLinkedinSquare} 
  \href{https://github.com/shajalahamedcse}{\faGithub}
  \href{https://medium.com/@shajalahamedcse}{\faMedium}
  \href{https://stackoverflow.com/users/5609026/shajal-ahamed}{\faStackOverflow}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  
    \resumeSubheading
      {Chittagong University of Engineering and Technology} { Chittagong, Bangladesh}
      {Bachelor of Science in Computer Science and Engineering.}{ 2011 - Present}


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: {Python}, {Golang}, {Javascript}}
     \hfill
   }
   \item{
   \textbf{Technologies}{: Docker, Kubernetes, Jenkins, Terraform, AWS,GCP Azure  }
   }
 \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
\smallskip
  \resumeSubHeadingListStart
 	  \resumeSubheading
      {\href{https://brilliant.com.bd/}{AirAsia}}{Federal Territory of Kuala Lumpur, Malaysia}
      {DevOps Engineer(II)}{Feb 2021 - Present}
      \resumeItemListStart
       \resumeItem{\href{https://www.airasiabig.com/}{AirAsiaBig}}{Currently my responsibility is to manage multiple projects of airasiabig hosted in AWS and GCP. I use IAC(Terraform) as main tool for infrastructure provision and change. Most of the applications are containerised and runs in kubernetes clusters. There is also CI/CD pipeline to deploy those container in different environment. Also, developing SOPs for improved troubleshooting and operational practices is another day to day task.If there is any kind of migration needed my job is also strategies and execute that.
       }

	 \smallskip
	  \resumeSubHeadingListEnd
  \smallskip
	   \resumeSubheading
      {\href{https://tecognize.com/training/}{Tecognize Training}}{Dhaka}
      {Lead Instructor}{July 2020 - Present}
      \resumeItemListStart
       \resumeItem{\href{}{DevOps and Software Engineering Course }}{I usually conduct various courses about kubernetes, docker, AWS and python.Already taught more than hundreds people around the world.
      }
       
	 \smallskip
	  \resumeSubHeadingListEnd
	   \resumeSubheading
      {\href{http://www.kloudlab.org/}{Kloudlab.org }}{Dhaka}
      {Cofounder and CTO}{July 2020 - Present}
      \resumeItemListStart
       \resumeItem{\href{http://www.kloudlab.org/}{Kloudlab Platform }}{Creating Kloudlab Platform from scratch.It is an online cloud and computer science learning platform.Our student use this platform for docker,kubernetes and cloud learning. Any student can launch lab based on credit,then the platform will create lab( in AWS,Azure,GCP) for him. Then he/she can do all kinds of hands on  from this platform.
       }
       
	 \smallskip
	  \resumeSubHeadingListEnd
	  \resumeSubheading
      {\href{https://brilliant.com.bd/}{InterCloud Ltd.}}{Dhaka}
      {Senior Software Engineer}{July 2019 - Jan 2021}
      \resumeItemListStart
       \resumeItem{\href{https://bcp.brilliant.com.bd/}{Brilliant Cloud Platform}}{Implementing Brilliant Cloud Platform from scratch.This platform creates api call to our underlying infrastructure.Currently our users can create their own vpc, subnet and launch virtual machine form this platform. Platform user also can create firewall rule for virtual machine. I am using kubernetes to manage this whole platform. .
       }
       \resumeItem{\href{https://bcp.brilliant.com.bd/}{Users VM Monitoring Service}}{Used kafka to monitor thousands of users vm. Deployed Kafka on kuberentes cluster and attached cinder volume with kafka to persist monitoring data. 
       }
	 \smallskip
	  \resumeSubHeadingListEnd
	  
	   \resumeSubheading
      {\href{https://evaly.com.bd/}{Evaly}}{Dhaka}
      {DevOps Consultant (Freelance)}{April 2020 - April 2020}
      \resumeItemListStart
       \resumeItem{Istio Deployment}{ Deployed all of their current microservices in kubernetes using istio.
       }
       \resumeItem{Custom Controller}{Wrote an custom controller that shut's down envoy sidecar after any kind of cornjob is done. }
      
       
	 \smallskip
       

	  \resumeSubHeadingListEnd
 \resumeSubheading
      {\href{https://selise.ch/}{SELISE rockin' software}}{Dhaka}
      {DevOps Consultant (Freelance)}{Nov 2019 - Dec 2019}
      \resumeItemListStart
       \resumeItem{Kubernetes Deployment}{ Used kubeadm to set up kubernetes in AWS and deployed hundreds of microservices in new cluster. Also helped with their infrastructure migration and service integration.
       }
       \resumeItem{Trainer}{Trained their devops team about managing the new deployment of kubernetes cluster.
       }
       \resumeItem{Automation and CI/CD}{Wrote new node provision and joining script for kubernetes in Ansible. Implemented docker build and deployment pipeline in jenkins.
       }
	 \smallskip
       

	  \resumeSubHeadingListEnd

	  
   \resumeSubheading
      {ITECH-SoftSolutions}{Khulna}
      {Senior DevOps Enigneer}{April 2019 - June 2019}
      \resumeItemListStart
       \resumeItem{Kubernetes}{Design,deploy and maintaining micro-services of multiple customers on Amazon EKS cluster.}
      \resumeItem{Monitoring}{Monitoring microservices using Promethues and Grafana. }
      \resumeItem{Logging, HPA}{Implemented HPA and NFS based logging system for container logging.}
        \resumeItem{CI/CD}
         {Writing fully automated CI/CD pipeline for docker build and deployment on kubernetes cluster.}
         \\

	  \resumeSubHeadingListEnd
    \resumeSubheading
      {Renata Ltd.}{Dhaka, Mirpur}
      {Senior Software Engineer}{Mar. 2017 - Mar. 2019}
      \resumeItemListStart
        \resumeItem{RenataVisio}{An Industrial IOT project that scrapes  sensor and  actuator data and saves the scarped data into Influxdb.\\
	 }
	 \smallskip
	  
 
      \resumeItem{Notification System}
          {This service is used for sending push notifications to the maintenance engineer about sensor and actuator malfunction. It is connected with RenataVisio's data pipeline so that it can send notification promptly.}
          \smallskip
    \resumeItem{Type-ahead Suggestion System}
          {One can not memorize all sensors and actuators model name. Trie data-structure is used for this suggestion system. So RenataVisio's sensor searching panel will guide someone to find sensor name and quantity from our four thousand sensors inventory database.}
      \resumeItemListEnd

   
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Achievements}
 \resumeSubHeadingListStart
	 \item  \textbf{iARC-2012}\\
	     \smallskip 
	  \hspace{20pt}{Champion in  Bangladesh Round.}\\
	  \hspace{20pt}{Fourth Position in International Round. (IIT, Kanpur)}
  \resumeSubHeadingListEnd



\section{Reference}
 \resumeSubHeadingListStart
  \item  \textbf{Mohammad Shamsul Arefin} \\Assistant Professor, Department of Computer Science and Engineering, CUET\\
  \href{mailto:sarefin@cuet.ac.bd}{\textbf{sarefin@cuet.ac.bd}}  \\
  Mobile : +8801766529027 \\
   
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
